\section*{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}
\addcontentsline{toc}{section}{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}

\begingroup
\renewcommand{\section}[2]{}
\begin{thebibliography}{}
	\bibitem{statistics} Video Streaming Market Size, Market Research Report [Электронный ресурс]. -- Режим доступа: https://www.fortunebusinessinsights.com/video-streaming-market-103057 (Дата обращения: 02.12.2023)
	
	\bibitem{genaralDefifnitionAttack} Боршевников, А. Е. Сетевые атаки. Виды. Способы борьбы / А. Е. Боршевников. — Текст : непосредственный // Современные тенденции технических наук : материалы I Междунар. науч. конф. (г. Уфа, октябрь 2011 г.). — Уфа : Лето, 2011. — С. 8-13. — URL: https://moluch.ru/conf/tech/archive/5/1115/ (дата обращения: 22.10.2022).
	
	\bibitem{smthAboutEmailBombing} Maroofi S. et al. Adoption of email anti-spoofing schemes: a large scale analysis //IEEE Transactions on Network and Service Management. – 2021. – Т. 18. – №. 3. – С. 3184-3196.
	
	\bibitem{kasperskyDDoS} Как работает DDoS-атака [Электронный ресурс]. -- Режим доступа: 
	\bibitem{behavior} Debar H., Dacier M., Wespi A. Towards a taxonomy of intrusion-detection systems // Computer Networks. 1999.
	
	\bibitem{DDoSMachineLearning} Thakkar A., Lohiya R. Attack classification using feature selection techniques: a comparative study //Journal of Ambient Intelligence and Humanized Computing. – 2021. – Т. 12. – №. 1. – С. 1249-1266.
	
	\bibitem{DDoSMachineLearning2} Awan M. J. et al. Real-time DDoS attack detection system using big data approach //Sustainability. – 2021. – Т. 13. – №. 19. – С. 10743.
	
	\bibitem{routing} Wang B., Lu K., Chang P. Design and implementation of Linux firewall based on the frame of Netfilter/IPtable //2016 11th International Conference on Computer Science \& Education (ICCSE). – IEEE, 2016. – С. 949-953.
	
	\bibitem{routing_2} Xuan L., Wu P. The optimization and implementation of iptables rules set on linux //2015 2nd International Conference on Information Science and Control Engineering. – IEEE, 2015. – С. 988-991.
	
	\bibitem{iptable} Руководство по iptables (Iptables Tutorial 1.1.19) [Электронный ресурс]. -- Режим доступа: http://www.opennet.ru/docs/RUS/iptables/ (Дата обращения: 01.05.2023)	
	
	\bibitem{syncookies} SYN cookies [Электронный ресурс]. -- Режим доступа: https://cr.yp.to/syncookies.html (Дата обращения: 17.06.2023)	
	
	\bibitem{syncookie_code} SYN cookies source code [Электронный ресурс]. -- Режим доступа: https://elixir.bootlin.com/linux/v6.2/source/net/ipv4/syncookies.c (Дата обращения: 02.09.2023)	
	
\end{thebibliography}
\endgroup

\pagebreak